---
title: "Rootpoint Distribution"
author: "Filipa Torrão & Eugenia Chiappe"
date: "`r Sys.Date()`"
output:
  html_document: default
editor_options: 
  chunk_output_type: console
---
## Load Libraries
```{r}
library(tibble)
library(fafbseg)
#if (!require("devtools")) install.packages("devtools")
#devtools::install_github("jefferislab/catnat")
library(catnat)
library(ggpubr)
library(dplyr)
library(tidyr)
library(stringr)

# Create the output directory (two levels above) for plots and CSV files
output_dir <- file.path("..", "..", "results","r_results","04_rootpoint_analysis")
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}
```

## Connect to Catmaid and Read bIPS Neuron
```{r}
conn = catmaid_login(server="https://fafb.catmaid.virtualflybrain.org/")
bips_fafbseg<- read.neuron.catmaid(3029743)
bips_points_fafbseg<- xyzmatrix(bips_fafbseg[["d"]]) #gets the xyz matrix for all the bips points
syn_from_bips<- filter(catmaid_get_connector_table(c(9730353,3029743)), direction=="incoming") #gets all incoming synapses onto bips
h2rn_syn_catmaid<-filter(syn_from_bips, partner_skid=='8178073'|
                           partner_skid=='8438889'|
                           partner_skid=='9730353'|
                           partner_skid=='11930921'|
                           partner_skid=='11956980'|
                           partner_skid=='12036568', confidence >3) %>% select(matches("[xyz]")) %>% xyzmatrix()
kd_catmaid_h2rn_fafbseg<-nabor::knn(query = h2rn_syn_catmaid, data=bips_points_fafbseg, k=1)
```

## Load H2RN Neurons and Combine Their Points
```{r}
#find the closest h2rn node to each h2rn-> bips and h2rn-> h2 synapse

h2rn_1_fafbseg<- read.neuron.catmaid(8178073)
h2rn_1_points_fafbseg<- xyzmatrix(h2rn_1_fafbseg[["d"]])
h2rn_2_fafbseg<- read.neuron.catmaid(8438889)
h2rn_2_points_fafbseg<- xyzmatrix(h2rn_2_fafbseg[["d"]])
h2rn_3_fafbseg<- read.neuron.catmaid(9730353)
h2rn_3_points_fafbseg<- xyzmatrix(h2rn_3_fafbseg[["d"]])
h2rn_4_fafbseg<- read.neuron.catmaid(11930921)
h2rn_4_points_fafbseg<- xyzmatrix(h2rn_4_fafbseg[["d"]])
h2rn_5_fafbseg<- read.neuron.catmaid(11956980)
h2rn_5_points_fafbseg<- xyzmatrix(h2rn_5_fafbseg[["d"]])
h2rn_6_fafbseg<- read.neuron.catmaid(12036568)
h2rn_6_points_fafbseg<- xyzmatrix(h2rn_6_fafbseg[["d"]])

h2rn_points_fafbseg<- rbind(h2rn_1_points_fafbseg,
                            h2rn_2_points_fafbseg,
                            h2rn_3_points_fafbseg,
                            h2rn_4_points_fafbseg,
                            h2rn_5_points_fafbseg,
                            h2rn_6_points_fafbseg)
```

## Get Synapse Data for H2, HS, and bIPS
```{r}
syn_to_h2<- filter(catmaid_get_connector_table(5232902), direction=="incoming")
syn_to_hs_1<-  filter(catmaid_get_connector_table(830793), direction=="incoming")
syn_to_hs_2<-  filter(catmaid_get_connector_table(827034), direction=="incoming")
syn_to_hs_3<-  filter(catmaid_get_connector_table(4058824), direction=="incoming")
syn_to_hs<- rbind(syn_to_hs_1,syn_to_hs_2,syn_to_hs_3)
syn_to_bips<- syn_from_bips
syn_to_bips_real<- filter(catmaid_get_connector_table(3029743), direction=="incoming")
```

## Prepare Synapse Matrices and KNN Searches
```{r}
h2rn_syn_to_bips<- h2rn_syn_catmaid

h2rn_syn_to_h2<- filter(syn_to_h2, partner_skid=='8178073'|
                          partner_skid=='8438889'|
                          partner_skid=='9730353'|
                          partner_skid=='11930921'|
                          partner_skid=='11956980'|
                          partner_skid=='12036568', confidence >3) %>% select(matches("[xyz]")) %>% xyzmatrix()
h2rn_syn_to_hs<- filter(syn_to_hs, partner_skid=='8178073'|
                          partner_skid=='8438889'|
                          partner_skid=='9730353'|
                          partner_skid=='11930921'|
                          partner_skid=='11956980'|
                          partner_skid=='12036568', confidence >3) %>% select(matches("[xyz]")) %>% xyzmatrix()
h2_syn_to_bips<- filter(syn_to_bips_real, partner_skid=="5232902",confidence >3) %>% select(matches("[xyz]")) %>% xyzmatrix()

#from the h2rn nodes closest to each synapse, get the closest 3 nodes (also from the h2rn skeleton)
kd_h2rn_bips<- nabor::knn(query = h2rn_syn_to_bips, data=h2rn_points_fafbseg, k=5)
kd_h2rn_h2<- nabor::knn(query = h2rn_syn_to_h2, data=h2rn_points_fafbseg, k=5)
kd_h2rn_hs<- nabor::knn(query = h2rn_syn_to_hs, data=h2rn_points_fafbseg, k=5)
kd_h2rn_h2_to_bips<- nabor::knn(query = h2_syn_to_bips, data=h2rn_points_fafbseg, k=5)

h2rn_bips_df<- as.data.frame(kd_h2rn_bips)
h2rn_bips_df<- rownames_to_column(h2rn_bips_df,'bips_idx')
h2rn_h2_df<- as.data.frame(kd_h2rn_h2)
h2rn_h2_df<- rownames_to_column(h2rn_h2_df,'h2_idx')
```

## Filter KNN Results Based on Distance
```{r}
test_df<- as.data.frame(kd_h2rn_h2_to_bips)
#keep only rows whose max distance (from any columns) is below the max(kd_h2rn_h2$nn.dists)
test_df<- rownames_to_column(test_df,'bips_idx')
df_kd_h2rn_h2_to_bips_filtered<- filter(test_df, nn.dists.1 < 2*max(kd_h2rn_h2$nn.dists) & nn.dists.2 < 2*max(kd_h2rn_h2$nn.dists) & 
                                          nn.dists.3 < 2*max(kd_h2rn_h2$nn.dists) & nn.dists.4 < 2*max(kd_h2rn_h2$nn.dists) &
                                          nn.dists.5 < 2*max(kd_h2rn_h2$nn.dists) )
not_close<- setdiff(test_df, df_kd_h2rn_h2_to_bips_filtered)
```

## Aggregating Synapses (H2 → bIPS)
```{r}
#aggregating really close synapses (h2->bips)
h2_to_bips_expanded<- select(df_kd_h2rn_h2_to_bips_filtered, c(nn.idx.1,nn.idx.2,nn.idx.3,nn.idx.4,nn.idx.5))

h2_to_bips_non_aggregated<- h2_to_bips_expanded
bips_non_aggregated<- as.data.frame(kd_h2rn_bips$nn.idx)
h2_non_aggregated<- as.data.frame(kd_h2rn_h2$nn.idx)

a<- as.data.frame(bips_non_aggregated)
b<- as.data.frame(h2_to_bips_non_aggregated)

x <- as.data.frame(expand.grid(seq(nrow(a)), seq(nrow(b))))

intersect_count<- c()
intersection_nodes<-data.frame()
non_intersection_nodes<- data.frame()

for (i in 1:nrow(x)){
  row<- as.numeric(x[i,])
  if (any(a[row[1],] %in% b[row[2],])){
    intersect_count[length(intersect_count)+1]<-1
    intersection_nodes<- rbind(intersection_nodes, c(a[row[1],],b[row[2],]))
  }
  else {
    intersect_count[length(intersect_count)+1]<-0
    non_intersection_nodes<- rbind(non_intersection_nodes, c(a[row[1],],b[row[2],]))
  }
}

number_close_syns_h2_bips<-sum(intersect_count)

split_by_h2<- split(intersect_count, ceiling(seq_along(intersect_count)/length(bips_non_aggregated$V1)))
split_by_h2_count<- as.data.frame(do.call(rbind,(lapply(split_by_h2, sum) )))
number_of_h2_syn_outside_bips_syn<- colSums(split_by_h2_count!=0)
```

## Intersection and Triangulation of Synapse Data
```{r}
number_h2rn_to_bips_in_bips_intersection<- distinct(select(intersection_nodes, c(V1,V2,V3,V4,V5)))
number_h2_to_bips_in_bips_intersection<- distinct(select(intersection_nodes, c(nn.idx.1,nn.idx.2,nn.idx.3,nn.idx.4,nn.idx.5)))

# Triangulation script
split_by_h2_close_to_bips<- as.data.frame(do.call(rbind,split_by_h2))
split_by_h2_close_to_bips<- split_by_h2_close_to_bips[rowSums(split_by_h2_close_to_bips[])>0,]

# finally intersecting all of them
a<- as.data.frame(h2_non_aggregated)
b<- as.data.frame(intersection_nodes)
x4 <- as.data.frame(expand.grid(seq(nrow(a)), seq(nrow(b))))
intersect_count_2<- c()
intersection_nodes_2<- data.frame()
non_intersection_nodes_2<- data.frame()
for (i in 1:nrow(x4)){
  row<- as.numeric(x4[i,])
  if (any(a[row[1],] %in% b[row[2],])){
    intersect_count_2[length(intersect_count_2)+1]<-1
    intersection_nodes_2<- rbind(intersection_nodes_2, cbind(a[row[1],],b[row[2],]))
  }
  else {
    intersect_count_2[length(intersect_count_2)+1]<-0
    non_intersection_nodes_2<- rbind(non_intersection_nodes_2, c(a[row[1],],b[row[2],]))
  }
}

number_close_syns_h2_bips_with_h2rn_nearby<-sum(intersect_count_2)
split_by_syn_sphere<- split(intersect_count_2, ceiling(seq_along(intersect_count_2)/length(h2_non_aggregated$V1)))
split_by_syn_sphere_count<- as.data.frame(do.call(rbind,(lapply(split_by_syn_sphere, sum) )))
number_of_syn<- colSums(split_by_syn_sphere_count!=0)
```

## Separate Intersecting vs Non-Intersecting Synapses
```{r}
number_h2rn_to_bips_in_total_intersection<- distinct(intersection_nodes_2[,6:10])
number_h2_to_bips_in_total_intersection<- distinct(intersection_nodes_2[,11:15])
number_h2rn_to_h2_in_total_intersection<- distinct(intersection_nodes_2[,1:5])

non_intersecting_h2rn_bips<- distinct(as.data.frame(cbind(non_intersection_nodes_2$V1,non_intersection_nodes_2$V2,non_intersection_nodes_2$V3,
                                                          non_intersection_nodes_2$V4,non_intersection_nodes_2$V5)))

intersection_nodes_2_h2rn_bips<-distinct(as.data.frame(cbind(intersection_nodes_2$V1,intersection_nodes_2$V2,intersection_nodes_2$V3,
                                                           intersection_nodes_2$V4,intersection_nodes_2$V5)))
real_non_intersecting_h2rn_bips<- setdiff(non_intersecting_h2rn_bips, intersection_nodes_2_h2rn_bips)

real_non_intersecting_h2rn_bips_single_id<- real_non_intersecting_h2rn_bips$V1

real_intersecting_h2rn_bips<- setdiff(intersection_nodes_2_h2rn_bips,real_non_intersecting_h2rn_bips) 

real_intersecting_h2rn_bips_single_id<- real_intersecting_h2rn_bips$V1

real_non_intersecting_h2rn_bips_single_id<- setdiff(real_non_intersecting_h2rn_bips_single_id,real_intersecting_h2rn_bips_single_id)
real_intersecting_h2rn_bips_single_id<- setdiff(real_intersecting_h2rn_bips_single_id,real_non_intersecting_h2rn_bips_single_id)
```

## Map Synapse Coordinates to bIPS and H2RN Skeleton
```{r}
kd_h2rn_bips_on_bips<- nabor::knn(query = h2rn_syn_to_bips, data=bips_points_fafbseg, k=1)
kd_h2rn_bips_one<- nabor::knn(query = h2rn_syn_to_bips, data=h2rn_points_fafbseg, k=1)

coordinates_on_bips_of_h2rn_syn_to_bips<- as.data.frame(bips_points_fafbseg[kd_h2rn_bips_on_bips$nn.idx ,])
coordinates_on_bips_of_h2rn_syn_to_bips$Idx<- kd_h2rn_bips_on_bips$nn.idx
coordinates_on_bips_of_h2rn_syn_to_bips<- rownames_to_column(coordinates_on_bips_of_h2rn_syn_to_bips, var = "Idx_syn")
coordinates_on_h2rn_of_h2rn_syn_to_bips<- as.data.frame(h2rn_points_fafbseg[kd_h2rn_bips_one$nn.idx ,])
coordinates_on_h2rn_of_h2rn_syn_to_bips$Idx<- kd_h2rn_bips_one$nn.idx
coordinates_on_h2rn_of_h2rn_syn_to_bips<- rownames_to_column(coordinates_on_h2rn_of_h2rn_syn_to_bips, var = "Idx_syn")
coordinates_on_h2rn_of_h2rn_syn_to_bips_non_intersection<- distinct(filter(coordinates_on_h2rn_of_h2rn_syn_to_bips, Idx %in% 
                                                                             real_non_intersecting_h2rn_bips_single_id))
h2rn_to_bips_syn_ids_non_intersecting<- coordinates_on_h2rn_of_h2rn_syn_to_bips_non_intersection$Idx_syn
coordinates_on_bips_of_h2rn_syn_to_bips_non_intersection<- filter(coordinates_on_bips_of_h2rn_syn_to_bips, Idx_syn %in%  h2rn_to_bips_syn_ids_non_intersecting)

coordinates_on_h2rn_of_h2rn_syn_to_bips_intersection<- distinct(filter(coordinates_on_h2rn_of_h2rn_syn_to_bips, Idx %in% 
                                                                         real_intersecting_h2rn_bips_single_id))
h2rn_to_bips_syn_ids_intersecting<- coordinates_on_h2rn_of_h2rn_syn_to_bips_intersection$Idx_syn
coordinates_on_bips_of_h2rn_syn_to_bips_intersection<- filter(coordinates_on_bips_of_h2rn_syn_to_bips, Idx_syn %in%  h2rn_to_bips_syn_ids_intersecting)
```

## Geodesic Distance Calculation and Mesh Graph Construction
```{r}
# geodesic distance calculation 
mesh2graph <- function(x, ...) {
  if(inherits(x, 'shapelist3d')) x=x[[1]]
  if(inherits(x, 'neuronlist')) x=x[[1]]
  if(!inherits(x, 'mesh3d')) x=as.mesh3d(x, ...)
  if(nrow(x$it)!=3) stop("I only work for triangular meshes right now")
  
  # make the edge list
  v1=x$it[1,]
  v2=x$it[2,]
  v3=x$it[3,]
  el=rbind(cbind(v1,v2), cbind(v1,v3), cbind(v2,v3))
  g=igraph::graph_from_edgelist(el, directed = FALSE)
  
  # calculate lengths of each edge
  xyz=xyzmatrix(x)
  edgelengths = function(v1, v2) {
    deltas=xyz[v1,,drop=F]-xyz[v2,,drop=F]
    sqrt(rowSums(deltas^2))
  }
  weights=c(edgelengths(v1,v2), edgelengths(v1,v3), edgelengths(v2,v3))
  igraph::E(g)$weight=weights
  g
}

bIPS.skid <- flywire_latestid('720575940622581173') #bips id
#flywire_latestid('720575940616243077', sample=FALSE)
#with_segmentation('sandbox', flywire_latestid('720575940625602908'))
# Load the segmented neuron
bIPS.mesh <- read_cloudvolume_meshes(bIPS.skid)
bips_mesh_graph<-mesh2graph(bIPS.mesh)

bIPS.AllInputs=flywire_partners(bIPS.skid, partners = 'inputs', details = TRUE, method='spine')

library(dplyr)
h2id=flywire_ids(flywire_latestid("720575940632427603"), integer64 = T)

h2rnids = flywire_ids(flywire_latestid(
  c(
    "720575940642076576",
    "720575940617566769",
    "720575940624756836",
    "720575940622082451",
    "720575940619291083",
    "720575940621865991"
    
  )
), integer64 = T)
hsids <- flywire_ids(flywire_latestid(c(
  "720575940635441771",
  "720575940631989571",
  "720575940626456894"
)), integer64 = T)

ulptcids <- flywire_ids(flywire_latestid(c(
  "720575940628599516",
  "720575940631296543",
  "720575940631333955",
  "720575940612144047", 
  "720575940606873522",
  "720575940647708537",
  "720575940626988053")), integer64 = T)
```

## 12. Process bIPS Inputs and Synapse Coordinates
```{r}
bIPS.selinputs <- bIPS.AllInputs %>%
  filter(cleft_scores>=50) %>%
  filter(pre_x<=(4*145680))%>% 
  # remove low probability synapses
  mutate(partner=case_when(
    pre_id==h2id ~ "H2",
    pre_id %in% h2rnids ~ "H2RN",
    pre_id %in% hsids ~ "HS",
    pre_id %in% ulptcids ~ "uLPTCrn",
    T ~ 'other'
  ))# %>%
#filter(partner!='other') #%

bIPS.selinputs %>%
  count(partner)

bips_mesh_graph<-mesh2graph(bIPS.mesh)

spike_generation_zone<- xyzmatrix(4*111653, 4*72308, 40*4974) #root point

coord_bips<- cbind(coordinates_on_bips_of_h2rn_syn_to_bips_non_intersection$X,coordinates_on_bips_of_h2rn_syn_to_bips_non_intersection$Y,
                   coordinates_on_bips_of_h2rn_syn_to_bips_non_intersection$Z)
coord_bips_inter<- cbind(coordinates_on_bips_of_h2rn_syn_to_bips_intersection$X,coordinates_on_bips_of_h2rn_syn_to_bips_intersection$Y,
                         coordinates_on_bips_of_h2rn_syn_to_bips_intersection$Z)


coord_bips_flywire<- fafb2flywire(coord_bips)
coord_bips_inter_flywire<- fafb2flywire(coord_bips_inter)

#these are the x y z coordinates for the synapses from neuron A/B onto the neuron of interest
x_y_z_matrix_h2<- filter(bIPS.selinputs, partner=='H2') %>% select(matches("post_[xyz]")) %>% xyzmatrix()
x_y_z_matrix_h2rn<- filter(bIPS.selinputs, partner=='H2RN') %>% select(matches("post_[xyz]")) %>% xyzmatrix()
x_y_z_matrix_hs<- filter(bIPS.selinputs, partner=='HS') %>% select(matches("post_[xyz]")) %>% xyzmatrix()
x_y_z_matrix_ulptcrn<- filter(bIPS.selinputs, partner=='uLPTCrn') %>% select(matches("post_[xyz]")) %>% xyzmatrix()
x_y_z_matrix_other<- filter(bIPS.selinputs, partner=="other"
) %>% select(matches("post_[xyz]")) %>% xyzmatrix()
x_y_z_matrix_h2rn_non_intersection<- coord_bips_flywire
x_y_z_matrix_h2rn_intersection<- coord_bips_inter_flywire
```

## Sample and Compute KNN for Synapse Distances
```{r}
n_h2rn_inputs_onto_bips<- nrow(x_y_z_matrix_h2rn)
set.seed(42)
x_y_z_matrix_other_229<- x_y_z_matrix_other[sample(nrow(x_y_z_matrix_other), n_h2rn_inputs_onto_bips, ), ]

kd_from_h2<- nabor::knn(query = x_y_z_matrix_h2, data=xyzmatrix(bIPS.mesh), k=1)
kd_from_h2rn<- nabor::knn(query = x_y_z_matrix_h2rn, data=xyzmatrix(bIPS.mesh), k=1)
kd_from_hs<- nabor::knn(query = x_y_z_matrix_hs, data=xyzmatrix(bIPS.mesh), k=1)
kd_from_ulptcrn<- nabor::knn(query = x_y_z_matrix_ulptcrn, data=xyzmatrix(bIPS.mesh), k=1)
kd_from_h2rn_non_intersection<- nabor::knn(query = x_y_z_matrix_h2rn_non_intersection, data=xyzmatrix(bIPS.mesh), k=1)
kd_from_h2rn_intersection<- nabor::knn(query = x_y_z_matrix_h2rn_intersection, data=xyzmatrix(bIPS.mesh), k=1)
kd_spike_generation_zone<- nabor::knn(query = spike_generation_zone, data=xyzmatrix(bIPS.mesh), k=1)
kd_from_other_random<- nabor::knn(query = x_y_z_matrix_other_229, data=xyzmatrix(bIPS.mesh), k=1)
```

## Calculate Geodesic Distances
```{r}
unique_ids_h2<- unique(kd_from_h2$nn.idx)
unique_ids_h2rn<-unique(kd_from_h2rn$nn.idx)
unique_ids_hs<-unique(kd_from_hs$nn.idx)
unique_ids_ulptcrn<-unique(kd_from_ulptcrn$nn.idx)
unique_ids_h2rn_non_intersection<- unique(kd_from_h2rn_non_intersection$nn.idx)
unique_ids_h2rn_intersection<- unique(kd_from_h2rn_intersection$nn.idx)
unique_ids_other_random<- unique(kd_from_other_random$nn.idx)
h2_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_h2, to = kd_spike_generation_zone$nn.idx, mode = "all")
hs_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_hs, to = kd_spike_generation_zone$nn.idx, mode = "all")
h2rn_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_h2rn, to = kd_spike_generation_zone$nn.idx, mode = "all")
h2rn_non_intersection_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_h2rn_non_intersection, to = kd_spike_generation_zone$nn.idx, mode = "all")
h2rn_intersection_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_h2rn_intersection, to = kd_spike_generation_zone$nn.idx, mode = "all")
ulptcrn_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_ulptcrn, to = kd_spike_generation_zone$nn.idx, mode = "all")
other_random_2_spike<- igraph::distances(bips_mesh_graph, v=unique_ids_other_random, to = kd_spike_generation_zone$nn.idx, mode = "all")
```
## Visualization of Geodesic Distances
```{r}
####--- Visualization for geodesic dist---####
df_h2_2_spike<-as.data.frame(as.matrix( c(apply(h2_2_spike, 1, c)) ))
df_h2_2_spike$Cell<- "H2"

df_hs_2_spike<-as.data.frame(as.matrix( c(apply(hs_2_spike, 1, c)) ))
df_hs_2_spike$Cell<- "HS"

df_h2rn_2_spike<-as.data.frame(as.matrix( c(apply(h2rn_2_spike, 1, c)) ))
df_h2rn_2_spike$Cell<- "H2rn"

df_h2rn_non_2_spike<-as.data.frame(as.matrix( c(apply(h2rn_non_intersection_2_spike, 1, c)) ))
df_h2rn_non_2_spike$Cell<- "H2rn (far from H2->bIPS)"

df_h2rn_inter_2_spike<-as.data.frame(as.matrix( c(apply(h2rn_intersection_2_spike, 1, c)) ))
df_h2rn_inter_2_spike$Cell<- "H2rn (part of triad)"

df_ulptcrn_2_spike<-as.data.frame(as.matrix( c(apply(ulptcrn_2_spike, 1, c)) ))
df_ulptcrn_2_spike$Cell<- "uLPTCrn"

df_other_random_2_spike<-as.data.frame(as.matrix( c(apply(other_random_2_spike, 1, c)) ))
df_other_random_2_spike$Cell<- "Random"

spike_combined<- rbind(df_h2_2_spike,df_hs_2_spike,df_h2rn_2_spike,df_h2rn_non_2_spike,df_h2rn_inter_2_spike,df_other_random_2_spike,df_ulptcrn_2_spike)
spike_combined$Distance<-as.numeric(spike_combined$V1)
p1 <- ggplot( spike_combined, aes(x=Distance, fill= Cell)) +
  geom_density( color="#e9ecef", alpha=0.6, position = 'identity') +
  scale_fill_manual(values=c("#69b3a2", "#404080","darkorange2","darkmagenta","burlywood3","thistle","firebrick4"))+#+ xlim(0,5000)
  ggtitle("Geodesic distance between the root point of bIPS and input from H2/HS/H2rn onto bIPS")
print(p1)
ggsave(filename = file.path(output_dir, "Geodesic distance.png"), plot = p1, width = 6, height = 4)


p2 <- ggviolin(spike_combined, x = "Cell", y = "Distance", fill = "Cell",
         palette = c("#69b3a2", "#404080","darkorange2","darkmagenta","burlywood3","thistle","firebrick4"),
         add = "boxplot", add.params = list(fill = "white"))
print(p2)
ggsave(filename = file.path(output_dir, "Violin Plots.png"), plot = p2, width = 12, height = 8)

```


## Statistical Analysis
```{r}
###Statistics###

res <- t.test(as.numeric(df_h2rn_inter_2_spike$V1), as.numeric(df_h2rn_non_2_spike$V1), var.equal = FALSE)
```

## Final Check of Coordinate Differences
```{r}
checking_if_different<- intersect(as.data.frame(coord_bips_flywire),as.data.frame(coord_bips_inter_flywire))
```





